Coupling the Level Set Method to Moments and Particles for Computing N-phase flows with phase change.

### 2024-05-19 CouplingLevelSetToMomentsAndParticles_paper/CouplingLevelSetToMomentsAndParticles.tex
talk notes

%% Use figure environment to create figures
%% Refer following link for more details.
%% https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions
%\begin{figure}[t]%% placement specifier
%% Use \includegraphics command to insert graphic files. Place graphics files in 
%% working directory.
%\centering%% For centre alignment of image.
%\includegraphics{example-image-a}
%% Use \caption command for figure caption and label.
%\caption{Figure Caption}\label{fig1}
%% https://en.wikibooks.org/wiki/LaTeX/Importing_Graphics#Importing_external_graphics
%\end{figure}
\section{Introduction}
\textcolor{red}{add table: existing multiphase flow MOF methods with surface tension, report curvature algorithm}
%does curvature discretization in conjunction with MOF exhibit checkerboard instability?

@@

\par\noindent
Ghost Fluid Method for surface tension \cite{kang2000boundary}:
\begin{eqnarray*}
\frac{p_{I,L}-p_{L}}{\rho_{L}\theta_{L}\Delta x}=
\frac{p_{R}-p_{I,R}}{\rho_{R}\theta_{R}\Delta x}
\end{eqnarray*}

@@

\par\noindent
Slope reconstruction using level set function, particles, centroid and
volume fraction:
\begin{eqnarray*}
 \phi(\vec{x})=\vec{n}\cdot(\vec{x}-\vec{x}_{0})+b
\end{eqnarray*}
\begin{eqnarray*}
(\vec{n},b)=\mbox{argmin}
 \sum_{ijk}\delta(||\vec{x}_{ijk}-\vec{x}^{c}||)
 (\phi(\vec{x}_{ijk})-\phi_{ijk})^{2}+
 \sum_{p}\delta(||\vec{x}_{p}-\vec{x}^{c}||)
 (\phi(\vec{x}_{p})-\phi_{p})^{2}
\end{eqnarray*}

	\subsection{Cell Integrated Semi-Lagrangian}\label{CISL}
	The following Cell Integrated Semi-Lagrangian (CISL) procedures are implemented and terms discretized as in \cite{pei2019hierarchical, LiETAL2015IncompressibleMultiphase,VAHAB2021}. This method follows an operator-splitting approach. The steps listed below are solved by the conservative  Weymouth and Yue \cite{WeymouthYue2010conservative}, or alternatively, the Euler Implicit-Lagrange Explicit (EI-LE) \cite{scardovelli2003interface,aulisa2007DirSplit} directionally-split methods.

>>>>

%% Use figure environment to create figures
%% Refer following link for more details.
%% https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions
%\begin{figure}[t]%% placement specifier
%% Use \includegraphics command to insert graphic files. Place graphics files in 
%% working directory.
%\centering%% For centre alignment of image.
%\includegraphics{example-image-a}
%% Use \caption command for figure caption and label.
%\caption{Figure Caption}\label{fig1}
%% https://en.wikibooks.org/wiki/LaTeX/Importing_Graphics#Importing_external_graphics
%\end{figure}
\section{Introduction}

\par\noindent
Incompressible multiphase flow and encapsulation simulations using the moment-of-fluid method, Li, Guibo and Lian, Yongsheng and Guo, Yisen and Jemison, Matthew and Sussman, Mark and Helms, Trevor and Arienti, Marco
\par\noindent
An {Improved} {Coupled} {Level} {Set} and {Continuous} {Moment}-of-{Fluid} {Method} for {Simulating} {Multiphase} {Flows} with {Phase} {Change},
Ye, Zhouteng and Estebe, Cody and Liu, Yang and Vahab, Mehdi and Huang, Zeyu and Sussman, Mark and Moradikazerouni, Alireza and Shoele, Kourosh and Lian, Yongsheng and Ohta, Mitsuhiro and Hussaini, M. Yousuff
\par\noindent
Fluid-structure interaction of thin flexible bodies in multi-material multi-phase systems
Mehdi Vahab and Mark Sussman and Kourosh Shoele
\par\noindent
FabricMask paper
\par\noindent

A boundary condition capturing method for multiphase incompressible flow
Kang, Myungjoo and Fedkiw, Ronald P and Liu, Xu-Dong
\par\noindent
MOF Reconstruction
\par\noindent
checkerboard instability
\par\noindent
CMOF Reconstruction
\par\noindent
Decision tree table time consuming to build, not generalizable to 
unstructured grids.
\par\noindent
PLSMOF Reconstruction
\par\noindent
Show results and animations: liquid lens, gas lens, tank, freezing

\textcolor{red}{add table: existing multiphase flow MOF methods with surface tension, report curvature algorithm}
%does curvature discretization in conjunction with MOF exhibit checkerboard instability?

@@

\newpage
\par\noindent
Ghost Fluid Method for surface tension \cite{kang2000boundary}:
\begin{eqnarray*}
\frac{p_{I,L}-p_{L}}{\rho_{L}\theta_{L}\Delta x}=
\frac{p_{R}-p_{I,R}}{\rho_{R}\theta_{R}\Delta x}
\end{eqnarray*}

@@

\newpage

\par\noindent
Slope reconstruction using level set function, particles, centroid and
volume fraction:
\begin{eqnarray*}
 \phi(\vec{x})=\vec{n}\cdot(\vec{x}-\vec{x}_{0})+b
\end{eqnarray*}
\begin{eqnarray*}
(\vec{n},b)=\mbox{argmin}
 \sum_{ijk}\delta(||\vec{x}_{ijk}-\vec{x}^{c}||)
 (\phi(\vec{x}_{ijk})-\phi_{ijk})^{2}+
 \sum_{p}\delta(||\vec{x}_{p}-\vec{x}^{c}||)
 (\phi(\vec{x}_{p})-\phi_{p})^{2}
\end{eqnarray*}
Replace the least squares $b$ with that which is derived from the 
reference volume fraction $F^{ref}$:
\begin{eqnarray*}
\mbox{VOLFRAC}(\vec{n},b^{ref})=\mbox{VOLFRAC}^{ref}
\end{eqnarray*}

\newpage
	\subsection{Cell Integrated Semi-Lagrangian}\label{CISL}
	The following Cell Integrated Semi-Lagrangian (CISL) procedures are implemented and terms discretized as in \cite{pei2019hierarchical, LiETAL2015IncompressibleMultiphase,VAHAB2021}. This method follows an operator-splitting approach. The steps listed below are solved by the conservative  Weymouth and Yue \cite{WeymouthYue2010conservative}, or alternatively, the Euler Implicit-Lagrange Explicit (EI-LE) \cite{scardovelli2003interface,aulisa2007DirSplit} directionally-split methods.
